\documentclass[12pt]{article}
%\usepackage{fullpage}
\usepackage{epic}
\usepackage{eepic}
\usepackage{paralist}
\usepackage{graphicx}
\usepackage{algorithm,algorithmic}
\usepackage{tikz}
\usepackage{xcolor,colortbl}
\usepackage{wrapfig}
\usepackage{amsmath}
\usepackage{xspace}


\newcommand{\sjava}{{\sc SJava}\xspace}
\newcommand{\lsub}[1]{\mathcal{L}_{\textsc{#1}}}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% This is FULLPAGE.STY by H.Partl, Version 2 as of 15 Dec 1988.
% Document Style Option to fill the paper just like Plain TeX.

\typeout{Style Option FULLPAGE Version 2 as of 15 Dec 1988}

\topmargin 0pt
\advance \topmargin by -\headheight
\advance \topmargin by -\headsep

\textheight 8.9in

\oddsidemargin 0pt
\evensidemargin \oddsidemargin
\marginparwidth 0.5in

\textwidth 6.5in
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\pagestyle{empty}
\setlength{\oddsidemargin}{0in}
\setlength{\topmargin}{-0.8in}
\setlength{\textwidth}{6.8in}
\setlength{\textheight}{9.5in}


\def\ind{\hspace*{0.3in}}
\def\gap{0.1in}
\def\bigap{0.25in}
\newcommand{\Xomit}[1]{}
\newcommand{\Mod}[1]{\ (\mathrm{mod}\ #1)}


\begin{document}

\setlength{\parindent}{0in}
\addtolength{\parskip}{0.1cm}
\setlength{\fboxrule}{.5mm}\setlength{\fboxsep}{1.2mm}
\newlength{\boxlength}\setlength{\boxlength}{\textwidth}
\addtolength{\boxlength}{-4mm}
\begin{center}\framebox{\parbox{\boxlength}{{\bf
CS 4820, Spring 2019 \hfill Homework 9, Problem 2}\\
% TODO: fill in your own name, netID, and collaborators
Name: \\
NetID: \\
}}
\end{center}
\vspace{5mm}
\vskip \bigap
{\bf (2)} {\em (10 points)} As you probably know, buffer overflows
are a common security flaw in computer programs that can be exploited
by attackers to overwrite areas of memory that should have been
protected from access. This exercise explores why it's so difficult
to perform static analysis of programs to discover potential buffer
overflows. In each of the sub-questions below, we use the term
{\em buffer program} to refer to an \sjava program whose base
function contains a variable named ``buffer'' of string type.
The {\em length of the buffer} refers to the number of characters
in this string.

For each of the folloiwng decision problems, determine whether the
problem is decidable, recognizable but not decidable,
or not recognizable. Substantiate your answer with a proof.
If one part of your solution uses material from
an earlier part, it is fine to refer back to that earlier
part of  your solution rather than repeating the material.


\vskip \gap
{\bf (2a)} {\em (5 points)} $\lsub{A}$ is the set of all ordered
triples $\langle M, x, k \rangle$ such that $M$ is a buffer program,
and when $M$ runs on input $x$ the length of the  buffer
exceeds $k$ at least once during its execution.

\vskip \gap
{\bf (2b)} {\em (5 points)} $\lsub{B}$ is the set of all ordered
pairs $\langle M, x \rangle$ such that $M$ is a buffer program,
and when $M$ runs on input $x$ the length of the buffer grows
unboundedly large. (Meaning: $M$ runs forever on input $x$,
and for all $k$ there is a time during its execution when the
length of the buffer exceeds $k$.)


%% Your solution goes here.


\end{document}
